\headingfont University of Extremadura\\ Faculty of Science\\[1cm] \textbf{ Physics degree\\ Degree Final Project\\[3cm] \flushleft{\large{About implementation of LoRa-based wireless monitoring systems for tree species dendrometry.}}\\[3cm] }

### 2020-06-08 docs/paper/LaTex/Paper.tex
Completing docs

% To make quotes (I need renewcommand for mkbegdispquote and mkenddispquote to enable quote marks at the
% end and beginning to displayquote environment. More info: https://tex.stackexchange.com/questions/101809/how-to-force-csquotes-to-show-the-quotations-marks-in-block-quotes)
\usepackage[style=english]{csquotes}
\renewcommand{\mkbegdispquote}[2]{\openautoquote}
\renewcommand{\mkenddispquote}[2]{\closeautoquote#1#2}
\renewcommand{\mkcitation}[1]{ #1}

@@

This is more or less, the definition of the IoT (Internet of Things) concept; according to \cite{IoTOverview} IoT concept comes from an earlier concept called M2M (Machine-to-Machine) communications. However, also according to \cite{IoTOverview} there is not an official definition for IoT concept, but

\begin{displayquote}[\cite{IoTObjetives}]
  based on the traditional information carriers including the Internet, telecommunication  network  and  so  on,  Internet  of Things (IoT) is a network that interconnects ordinary physical  objects  with  the identifiable addresses  so that provides intelligent services.  
\end{displayquote}

@@

\begin{displayquote}
  The measuring of the diameter of standing trees from the ground with a dendrometer that can also be used to measure tree heights.
\end{displayquote}

@@

\subsection{Arduino, multipurpose microcontroller}
It's not difficult to justify the use of such an interesting platform as Arduino. The adaptability is one of its strengths, therefore; it is able to acquire and process certain data coming from a set of sensors and manage it to send this via any plugged wireless network interface.

@@

\subsection{LoRa (Long Range)}
LoRa is a \enquote{long-range, low-power, low-bitrate, wireless telecommunications system}\cite{LoRaGeneral}. This is because some devices inside IoT paradigm tend to be economical and low-resources devices, in order to get them distributed/scattered, as it has been pointed. So this low availability along to their tendency to be distributed/scattered causes the necessity for a low-power consumption and a long-range telecommunication.

In a more general sense, there is a wider concept to include all these kind of technologies which fullfil the IoT communication requirements, this is the \enquote{Low-Power Wide Area Networks} (LPWAN)

\begin{displayquote}[\cite{LoRaGeneral}]
  Colloquially  speaking,  an LPWAN is supposed to be to the IoT what WiFi was to consumer networking: offering radio coverage over a (very) large area by way of base stations and adapting transmission rates, transmission power, modulation, duty cycles, etc., such that end-devices incur a very low energy consumption due to their being connected. 
\end{displayquote}

@@

\subsection{RaspberryPi, a powerful microcomputer}
As in the case of Arduino, RaspberryPi provides a powerful platform, however in the case of a RaspberryPi this platform is slightly more complex than for an Arduino.\footnote{There are a lot of Arduino models, and maybe some of them could be able to support, for example, multiple kind of Real Time Operative Systems, but it is not the case of this project, wherein the Arduino role is just to act as a core for the nodes.} From the hardware point of view, RaspberryPi implements a better one than Arduino, this also has an impact on a higher cost; however, this hardware allows a RaspberryPi to support a whole operating system; that's because this devices are usually called \textit{single-board computers}.

@@

\subsection{Dragino shields/hats}
These shields/expansion cards are necessary because those devices (Arduino and RaspberryPi) have not the ability to comunicate through LoRa physical layer, that's because they need a physical interface in order to manage those LoRa packages. Both shields are based on the SX1276/SX1278 transceiver. However the RaspberryPi hat also has a L80 GPS interface (Base on MTK MT3339), meanwhile Arduino has not.

@@

>>>>

% To make quotes (I need renewcommand for mkbegdispquote and mkenddispquote to enable quote marks at the
% end and beginning to displayquote environment. More info: https://tex.stackexchange.com/questions/101809/how-to-force-csquotes-to-show-the-quotations-marks-in-block-quotes)
\usepackage[style=english]{csquotes}
% \renewcommand{\mkbegdispquote}[2]{\openautoquote}
% \renewcommand{\mkenddispquote}[2]{\closeautoquote#1#2}
% \renewcommand{\mkcitation}[1]{ #1}

% Switching to quoting package (for block quotes, I still need csquotes for \enquote{})
\usepackage[begintext=``, endtext='']{quoting}
\quotingsetup{vskip=5pt}

@@

This is more or less, the definition of the IoT (Internet of Things) concept; according to \cite{IoTOverview} IoT concept comes from an earlier concept called M2M (Machine-to-Machine) communications. However, also according to \cite{IoTOverview} there is not an official definition for IoT concept, but according to \cite{IoTObjetives}

\begin{quoting}
  based on the traditional information carriers including the Internet, telecommunication  network  and  so  on,  Internet  of Things (IoT) is a network that interconnects ordinary physical  objects  with  the identifiable addresses  so that provides intelligent services.
\end{quoting}

@@

\begin{quoting}
  The measuring of the diameter of standing trees from the ground with a dendrometer that can also be used to measure tree heights.
\end{quoting}

@@

\subsection{Hardware}

\subsubsection{Arduino, multipurpose microcontroller}
It's not difficult to justify the use of such an interesting platform as Arduino. The adaptability is one of its strengths, therefore; it is able to acquire and process certain data coming from a set of sensors and manage it to send this via any plugged wireless network interface.

@@

\subsubsection{LoRa (Long Range)}
LoRa is a \enquote{long-range, low-power, low-bitrate, wireless telecommunications system}\cite{LoRaGeneral}. This is because some devices inside IoT paradigm tend to be economical and low-resources devices, in order to get them distributed/scattered, as it has been pointed. So this low availability along to their tendency to be distributed/scattered causes the necessity for a low-power consumption and a long-range telecommunication.

In a more general sense, there is a wider concept to include all these kind of technologies which fullfil the IoT communication requirements, this is the \enquote{Low-Power Wide Area Networks} (LPWAN), so as claimed by \cite{LoRaGeneral}

\begin{quoting}
  Colloquially  speaking,  an LPWAN is supposed to be to the IoT what WiFi was to consumer networking: offering radio coverage over a (very) large area by way of base stations and adapting transmission rates, transmission power, modulation, duty cycles, etc., such that end-devices incur a very low energy consumption due to their being connected.
\end{quoting}

@@

\subsubsection{RaspberryPi, a powerful microcomputer}
As in the case of Arduino, RaspberryPi provides a powerful platform, however in the case of a RaspberryPi this platform is slightly more complex than for an Arduino.\footnote{There are a lot of Arduino models, and maybe some of them could be able to support, for example, multiple kind of Real Time Operative Systems, but it is not the case of this project, wherein the Arduino role is just to act as a core for the nodes.} From the hardware point of view, RaspberryPi implements a better one than Arduino, this also has an impact on a higher cost; however, this hardware allows a RaspberryPi to support a whole operating system; that's because this devices are usually called \textit{single-board computers}.

@@

\subsubsection{Dragino shields/hats}
These shields/expansion cards are necessary because those devices (Arduino and RaspberryPi) have not the ability to comunicate through LoRa physical layer, that's because they need a physical interface in order to manage those LoRa packages. Both shields are based on the SX1276/SX1278 transceiver. However the RaspberryPi hat also has a L80 GPS interface (Base on MTK MT3339), meanwhile Arduino has not.

@@

\subsection{Software}

\subsubsection{FIWARE}
It is defined as \enquote{The Open Source Platform for Our Smart Digital Future}\cite{Fiware}; in a deeper sense is \enquote{an open source initiative defending an universal set of standards for context data management}\cite{Fiware}, which basically means that \textit{FIWARE} is an open source platform where develop IoT and smart solutions. The platform provides a number of software modules called \textit{Generic Enablers}; among all those \textit{Generic Enablers} there is one particularly important called \textit{Orion Context Broker}. In fact, for a solution to be considered as \textit{Powered by FIWARE} it must to use the \textit{Orion Context Broker} at least.

This \textit{Context data} is just a way to name any kind of data coming from any kind of sensor. \textit{Orion Context Broker} is designed to manage this context data through concepts such as \textit{subscriptions} or \textit{entities}, to name but a few; however, all these \textit{Generics Enablers} communicate with each other using the \textit{FIWARE NGSI RESTful API}\cite{NGSI}.\footnote{\textit{RESTful} term comes from the software architectural style \textit{REST}, which stands for \textit{Representational State Transfer}}
